### 2020-10-01 paper/natastron/paper.tex
Tidied up separate documents

\usepackage{chngcntr}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage[ ]{hyperref}
\graphicspath{{Images/}}
\usepackage[symbol]{footmisc}

@@

\textbf{Asteroseismic main sequence targets:} In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) oscillations for each star, of which the latter have significantly lower signal-to noise. Radial oscillations ($\ell = 0$), which are also visible, do not split. In this work, we studied a sample of 95 of the highest signal-to-noise targets observed by \textit{Kepler}, combining the `Kages' \cite{silvaaguirre+2015,davies+2016} and LEGACY \cite{lund+2017, silvaaguirre+2017} catalogues\footnote{For these catalogues the mode extraction through frequency fitting \cite{davies+2016, lund+2017} and modelling using mode frequencies to obtain stellar parameters \cite{silvaaguirre+2015, silvaaguirre+2017} are covered in separate papers.}. Further details on these data can be found in \textbf{Methods}.

@@

\input{si.tex}

>>>>

\usepackage{chngcntr}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage[ ]{hyperref}
\graphicspath{{Images/}}
%\usepackage[symbol]{footmisc}

@@

\textbf{Asteroseismic main sequence targets:} In order to obtain robust asteroseismic rotation rates, we required detections of multiples of both dipole (denoted as $\ell = 1$) and quadrupole ($\ell = 2$) p mode\footnote{\textit{Pressure} modes, the visible type of oscillation in main sequence stars} oscillations for each star, of which the latter have significantly lower signal-to noise. Radial oscillations ($\ell = 0$), which are also visible, do not split. In this work, we studied a sample of 95 of the highest signal-to-noise targets observed by \textit{Kepler}, combining the `Kages' \cite{silvaaguirre+2015,davies+2016} and LEGACY \cite{lund+2017, silvaaguirre+2017} catalogues\footnote{For these catalogues the mode extraction through frequency fitting \cite{davies+2016, lund+2017} and modelling using mode frequencies to obtain stellar parameters \cite{silvaaguirre+2015, silvaaguirre+2017} are covered in separate papers.}. Further details on these data can be found in \textbf{Methods}.

@@

### 2020-10-01 paper/natastron/si.tex
Tidied up separate documents

\clearpage
\section*{Supplementary Information}

\section*{Asteroseismic Model}\label{s:seismo}
In order to extract signatures of stellar rotation from the asteroseismic p mode frequencies, we built a model that simultaneously treats the convective background ($B(\nu)$), the oscillations ($O(\nu)$), and the white noise ($W$), where $\nu$ is frequency \cite{davies+2015}. Our data, observed with \kepler, are also subject to the apodization (attenuation) of signals in the frequency-domain, where we fit our model \cite{chaplin+2011}. The apodization in power is given by

@@

\subsection*{Convective Background ($B(\nu)$)}
To model the convective background we used three Harvey components \cite{harvey1985}, which express the background in power as Lorentzian-like functions centered on zero frequency. The Harvey components take the form

@@

\subsection*{Modes of Oscillation ($O(\nu)$)}
Modes of oscillation appear in the power spectrum as Lorentzian peaks \cite{chaplin+basu2017}. These peaks can be described by three values: the radial order ($n$, the overtone number of the oscillation), the angular degree ($\ell$) and the azimuthal order ($m$). Due to stellar rotation, each mode with an angular degree of $\ell > 0$ is split into its $(2\ell +1)$ Lorentzian components, labeled by $m$. For all $\ell=(0,1,2)$ modes identified for our targets in the  `Kages'  and LEGACY studies \cite{davies+2016,lund+2017} we add a (set of) Lorentzian(s) to our model, building a composite model representing all visible modes. The construction of our oscillation model takes the form

@@

\subsubsection*{Mode Frequencies and Rotational Splitting ($\nu_{n,\ell,m}$)}\label{ssec:frequencies}
The mode frequencies of main sequence stars are described by the asymptotic expression \cite{tassoul1980, vrard+2016}. The asymptotic expression defines the locations of the modes as regularly spaced, with structured deviation around \numax, the frequency of maximum oscillation amplitude. The expression takes the form

@@

\subsubsection*{Mode Linewidth ($\Gamma_{n,\ell}$)}
The linewidths of asteroseismic p modes vary roughly as a function of mode frequency, and do so slowly relative to \dnu. This can be expressed as an empirical relation \cite{davies+2014, appourchaux+2016, lund+2017}. However, this relation has six free parameters, none of which are directly relevant to this work. Instead of fitting this relation, we chose to employ a more flexible Gaussian Process \cite[GP]{rasmussen+williams2006} to act as a prior on the linewidths. This can be considered as us modelling the linewidths as correlated measurements, effectively loosely constraining how linewidth varies with frequency.

@@

\subsubsection*{Mode Heights and Angle of Inclination ($H_{n,\ell,m}$)}
The height in power of each mode, $H_{n, \ell, m}$, varies not only as a function of distance in frequency from \numax, but also due to observation conditions, such as inclination angle and passband. In our model, we treated $H_{n, \ell, m}$ as a deterministic parameter, as

@@

\subsection*{Likelihood Function for $M(\nu)$}\label{sec:like}
If data have Gaussian noise in the time domain, they will appear in the frequency domain with noise following a $\chi^2$ distribution with two degrees of freedom \cite[$\chi^2_2$ hereafter]{woodard1984}. The noise properties of $\chi^2_2$ distributed data are multiplicative, and require a specific treatment when fitting a model. As our frequency bins can be approximated to be independent, we used the likelihood function \cite{anderson+1990},

@@

\subsection*{Model preparation and hyperparameter priors}
\subsubsection*{Fitting the convective background}\label{sec:background}
Fitting the convective background, apodization and white noise component must be done for the full range of the power spectrum in order to be accurately constrained. However, fitting a single model to the full range of frequencies is computationally inefficient when we are interested in the modes of oscillation, as these occupy a relatively small range of frequencies.

@@

\subsubsection*{Obtaining First Guesses and Prior Values}
In order to utilise some of the prior measurements of our targets without using them as hard constraints on our parameters, some of our model equations were fit to LEGACY and `Kages' data to obtain first guesses and mean values on hyperparameter priors.

@@

\subsubsection*{Priors on our Hyperparameters}
Given our first guesses and measured prior values, we can define the prior probabilities of the hyperparameters on which our model depends. For the mode frequency hyperparameters (Eq. \ref{eq:asymptotic}), these are

@@

\subsection*{Fitting procedure}
Using our prior information and model described above, we fit Equation \ref{eq:model} to our data $\mathcal{P}$, using the likelihood function described in Section \ref{sec:like}.

@@

>>>>

\documentclass[12pt]{article}
\setlength{\textwidth}{167mm}
\setlength{\headsep}{0mm}
\setlength{\headheight}{0mm}
\setlength{\textheight}{230mm}
\setlength{\oddsidemargin}{1.6mm}
\setlength{\evensidemargin}{1.6mm}
\setlength{\topmargin}{4.6mm}

\usepackage{chngcntr}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage[ ]{hyperref}
\graphicspath{{Images/}}
%\usepackage[symbol]{footmisc}

% Astronomical abbreviations (thanks to Dan Huber)
\newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
\newcommand{\dnu}{\mbox{$\Delta \nu$}\xspace}
\newcommand{\muHz}{\mbox{$\mu$Hz}\xspace}
\newcommand{\teff}{\mbox{$T_{\rm eff}$}\xspace}
\newcommand{\logg}{\mbox{$\log(g)$}\xspace}
\newcommand{\feh}{\mbox{$\rm{[Fe/H]}$}\xspace}
\newcommand{\msun}{\mbox{$\mathrm{M}_{\odot}$}\xspace}
\newcommand{\lsun}{\mbox{$\mathrm{L}_{\odot}$}\xspace}
\newcommand{\mearth}{\mbox{$\mathrm{M}_{\oplus}$}\xspace}
\newcommand{\rsun}{\mbox{$\mathrm{R}_{\odot}$}\xspace}
\newcommand{\kepler}{\emph{Kepler}\xspace}
\newcommand{\tess}{\emph{TESS}\xspace}
\newcommand{\ktwo}{K2\xspace}
\newcommand{\gaia}{\emph{Gaia}\xspace}

\begin{document}

\section*{\underline{Supplementary Information}}
\tableofcontents

\section{Asteroseismic Model}\label{s:seismo}
In order to extract signatures of stellar rotation from the asteroseismic p mode frequencies, we built a model that simultaneously treats the convective background ($B(\nu)$), the oscillations ($O(\nu)$), and the white noise ($W$), where $\nu$ is frequency \cite{davies+2015}. Our data, observed with \kepler, are also subject to the apodization (attenuation) of signals in the frequency-domain, where we fit our model \cite{chaplin+2011}. The apodization in power is given by

@@

\subsection{Convective Background ($B(\nu)$)}
To model the convective background we used three Harvey components \cite{harvey1985}, which express the background in power as Lorentzian-like functions centered on zero frequency. The Harvey components take the form

@@

\subsection{Modes of Oscillation ($O(\nu)$)}
Modes of oscillation appear in the power spectrum as Lorentzian peaks \cite{chaplin+basu2017}. These peaks can be described by three values: the radial order ($n$, the overtone number of the oscillation), the angular degree ($\ell$) and the azimuthal order ($m$). Due to stellar rotation, each mode with an angular degree of $\ell > 0$ is split into its $(2\ell +1)$ Lorentzian components, labeled by $m$. For all $\ell=(0,1,2)$ modes identified for our targets in the  `Kages'  and LEGACY studies \cite{davies+2016,lund+2017} we add a (set of) Lorentzian(s) to our model, building a composite model representing all visible modes. The construction of our oscillation model takes the form

@@

\subsubsection{Mode Frequencies and Rotational Splitting ($\nu_{n,\ell,m}$)}\label{ssec:frequencies}
The mode frequencies of main sequence stars are described by the asymptotic expression \cite{tassoul1980, vrard+2016}. The asymptotic expression defines the locations of the modes as regularly spaced, with structured deviation around \numax, the frequency of maximum oscillation amplitude. The expression takes the form

@@

\subsubsection{Mode Linewidth ($\Gamma_{n,\ell}$)}
The linewidths of asteroseismic p modes vary roughly as a function of mode frequency, and do so slowly relative to \dnu. This can be expressed as an empirical relation \cite{davies+2014, appourchaux+2016, lund+2017}. However, this relation has six free parameters, none of which are directly relevant to this work. Instead of fitting this relation, we chose to employ a more flexible Gaussian Process \cite[GP]{rasmussen+williams2006} to act as a prior on the linewidths. This can be considered as us modelling the linewidths as correlated measurements, effectively loosely constraining how linewidth varies with frequency.

@@

\subsubsection{Mode Heights and Angle of Inclination ($H_{n,\ell,m}$)}
The height in power of each mode, $H_{n, \ell, m}$, varies not only as a function of distance in frequency from \numax, but also due to observation conditions, such as inclination angle and passband. In our model, we treated $H_{n, \ell, m}$ as a deterministic parameter, as

@@

\subsection{Likelihood Function for $M(\nu)$}\label{sec:like}
If data have Gaussian noise in the time domain, they will appear in the frequency domain with noise following a $\chi^2$ distribution with two degrees of freedom \cite[$\chi^2_2$ hereafter]{woodard1984}. The noise properties of $\chi^2_2$ distributed data are multiplicative, and require a specific treatment when fitting a model. As our frequency bins can be approximated to be independent, we used the likelihood function \cite{anderson+1990},

@@

\subsection{Model preparation and hyperparameter priors}
\subsubsection{Fitting the convective background}\label{sec:background}
Fitting the convective background, apodization and white noise component must be done for the full range of the power spectrum in order to be accurately constrained. However, fitting a single model to the full range of frequencies is computationally inefficient when we are interested in the modes of oscillation, as these occupy a relatively small range of frequencies.

@@

\subsubsection{Obtaining First Guesses and Prior Values}
In order to utilise some of the prior measurements of our targets without using them as hard constraints on our parameters, some of our model equations were fit to LEGACY and `Kages' data to obtain first guesses and mean values on hyperparameter priors.

@@

\subsubsection{Priors on our Hyperparameters}
Given our first guesses and measured prior values, we can define the prior probabilities of the hyperparameters on which our model depends. For the mode frequency hyperparameters (Eq. \ref{eq:asymptotic}), these are

@@

\subsection{Fitting procedure}
Using our prior information and model described above, we fit Equation \ref{eq:model} to our data $\mathcal{P}$, using the likelihood function described in Section \ref{sec:like}.

@@

\bibliographystyle{naturemag}
\bibliography{library.bib} %

\end{document}
